Fair Queuing Aware Congestion Control

### 2023-06-09 tex/paper.tex
Typos

>>>>

Since the subflow with the lower sending rate might experience lower queuing delay in case of fair queuing, it might be beneficial to include more important data in this subflow while the less urgent data can be sent in the subflow with the higher sending rate. This might, for example, be useful for cloud gaming: One could separate the video data into two parts: One part which includes a low resolution base video, which is transferred in the subflow with low queuing delay, while additional data, which increase the video quality, can be transferred in the subflow that might experience higher queuing delay.
